Estimating nucleon substructure properties in a\\[.2ex] unified model of p-Pb and Pb-Pb collisions

### 2018-05-08 talk/qm2018.tex
Remove all traces of the log transform
work on nucleon width correction

\title{Estimating nucleon substructure properties in a\\[.2ex]
unified hydrodynamic model of p-Pb and Pb-Pb collisions}
\author[J.\ S.\ Moreland]{\scshape J.\ S.\ Moreland, J.\ E.\ Bernhard \& S.\ A.\ Bass}
\institute[Duke]{\scshape Duke University}
\date{\scshape 14 May 2018}

@@

\begin{frame}{\scshape Flow in small systems}
  \smallskip
  \begin{columns}[T]
    \begin{column}{.62\textwidth}
      \bigskip
      Important questions:\\
      \begin{itemize}
        \item Is hydro applicable to small collision systems?
        \item If so, can we fit small system collectivity using current hydro models?
      \end{itemize}
      \smallskip
      First question precludes the second, but also more difficult to answer.\\[1ex]
      Let's tackle the second question \textit{assuming} hydrodynamic models make
      sense down to length scales $\Delta x=.2$~fm.\\[1ex]
      Under this assumption, does a unified hydrodynamic description of p+A and A+A data even exist?
    \end{column}
    \begin{column}{.3\textwidth}
      \centering
      \includegraphics[width=\columnwidth]{pbpb_corr2d}\\
      \includegraphics[width=\columnwidth]{ppb_corr2d}
    \end{column}
  \end{columns}

@@

\begin{frame}[t]{\scshape Nuclear structure}
  \begin{columns}[T]
    \begin{column}{.4\textwidth}
      \begin{figure}
        \includegraphics[width=.9\columnwidth]{pb208}\\
        Pb$^{208}$ nucleus
      \end{figure}
    \end{column}
    \begin{column}{.6\textwidth}
      \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{itemize}
        \item Sample nucleon radii from spherical or deformed Woods-Saxon distributions
        \item Euler angles resampled to preserve minimum nucleon distance
          $d_\mathrm{min}$ [fm]
        \item Gaussian nucleons of width $w$ [fm]
      \end{itemize}
      \medskip
      \textcolor{theme}{This work:}
      \begin{itemize}
        \item Trade Gaussian nucleons for lumpy nucleons
      \end{itemize}
      \begin{tikzpicture}[absolute, overlay]
        \node (a) at (2, -.75) {\includegraphics[scale=.5]{gaussian_proton}};
        \node[right=of a.east] (b) {\includegraphics[scale=.5]{deformed_proton}};
        \draw[->, thick] (a) -- (b);
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t, plain]{\scshape Nucleon substructure}
  \vspace{2em}
  \begin{columns}[t]
    \begin{column}{.2\textwidth}
      \centering \small Sampling radius
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw[thick] (0,0) circle [radius= 1cm] node (A) {\normalsize 1 fm};
          \draw[thick] (0,-2) circle [radius=.8cm] node (B) {\small .8 fm};
          \draw[thick] (0,-3.6) circle [radius=.6cm] node (C) {\scriptsize .6 fm};
          \draw [thick] (0,-4.8) circle [radius=.4cm] node (D) {\tiny .4 fm};
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.2\textwidth}
      \centering \small Parton width
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0, 0) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.3) circle (.6cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-2.2cm] circle (.4cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.2cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.2\textwidth}
      \centering \small Parton number
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0,0) circle (1cm);
          \foreach \theta/\radius in {
            36/0.48, 72/0.6, 108/0.6, 140/0.36, 172/0.12,
            190/0.6, 240/0.36, 272/0.6, 308/0.48, 360/0.6
          }{
            \draw [thick] ({\theta}:\radius) circle (.3cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-2.2cm] circle (.3cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 180}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.3cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.4\textwidth}
      \centering
      \textcolor{theme}{Free parameters:}\\[1ex]
      \begin{itemize}
        \small
        \item Width of the Gaussian distribution used to sample
          parton radial coordinates
        \item Number of Gaussian partons inside each nucleon
        \item Width of the Gaussian partons
      \end{itemize}
      \bigskip
      \textcolor{theme}{Absent from this work:}\\[1ex]
      \begin{itemize}
        \small
        \item Parton spatial correlations,\\
          see talk by Alba Soto Ontoso
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Cross sections}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics<1>[width=\textwidth]{trento_nucleons}
        \includegraphics<2>[width=\textwidth]{trento_participants}\\
        \small MC-Glauber cross sections\\
        (proton d.o.f. shown)
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{align*}
        P_\text{coll} &= 1 - \exp[-\sigma_{gg} T_{pp}(b)] \\
        \sigma_\text{nn}^\text{inel} &= \int 2\pi b\, db\, P_\text{coll}(b)
      \end{align*}
      \only<1>{\includegraphics<1>[scale=.8]{collision_profile}}
      \only<2>{
        \textcolor{theme}{This work:}
        \begin{equation*}
          P_\text{coll} \rightarrow 1 - \prod_{i,j=1}^{n_\text{part}}
          [1 - P_\text{coll}(b_{ij})]
        \end{equation*}
        Solve for opacity parameter $\sigma_{gg}$ numerically
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Participant thickness functions}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_thickness}
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{equation*}
        T_\text{nucleus}(x, y) = \sum\limits_{i=1}^{N_\text{part}}
        \gamma_i\, T_\text{proton}(x - x_i, y - y_i)
      \end{equation*}
      {\small Random weight $\gamma_i$ sampled from Gamma distribution with unit mean
      and variance $1/k$.}\\[2ex]
      \textcolor{theme}{This work:}
      \begin{equation*}
        \gamma_i\, T_\text{proton} \rightarrow \sum\limits_{j=1}^{N_\text{parton}}
        \gamma_j\,T_\text{parton} 
      \end{equation*}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Entropy deposition}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_entropy}
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Generalized Mean Ansatz:}
      \begin{equation*}
        \frac{dS}{d\eta} \propto T_R(T_A, T_B) \equiv
        \left(\frac{T_A^p + T_B^p}{2}\right)^{1/p}
      \end{equation*}
      \begin{equation*}
        T_R =
        \begin{cases}
          \max(T_A, T_B) & p \rightarrow +\infty, \\[.5ex]
          (T_A + T_B)/2 & p = +1, \\[.5ex]
          \sqrt{T_A T_B} & p = 0, \\[.5ex]
          2\, T_A T_B/(T_A + T_B) & p = -1, \\[.5ex]
          \min(T_A, T_B) & p \rightarrow -\infty.
        \end{cases}
      \end{equation*}
      \begin{center}
        \smallskip \small $T$ denotes \emph{participant} thickness function
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Free streaming}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_freestream}\\
        \small arrows: fluid velocity\\weighted by energy density
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Pre-equillibrium phase:}
      \begin{itemize}
        \small
        \item Massless non-interacting parton gas matched to viscous hydrodynamics
          \textcolor{theme}{\scriptsize PRC.91.064906, PRC.80.034902}.
        \item Must reinterpret initial entropy density as initial gluon density,\,
          $dN_g/y \sim dS/dy$
        \item Initialize hydro with non-zero $u^\mu$ and $\pi^{\mu\nu}$
      \end{itemize}
      \medskip
      \includegraphics{coupling}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Computer experiment design}
  \bigskip
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      \scriptsize
      \begin{tabular}{lll}
        Parameter         & Description                        & Range           \\
        \paddedhline
        Norm              & Overall normalization              & 12--28          \\
        $p$               & Entropy deposition parameter       & $-1$ to $+1$    \\
        $\sigmaf$         & Relative parton fluct. std.\       & 0--2            \\
        $w$               & Parton sampling radius             & 0.4--1.2 fm     \\
        $\X$              & Parton structure parameter         & 0--1            \\
        $\npartons$       & Number of partons                  & 1--10           \\
        $\dmin$           & Nucleon exclusion volume           & 0--4.9 fm$^3$   \\
        $\tau_{fs}$       & Free streaming time                & 0.1--1.5 fm/$c$ \\
        $\eta/s$ min      & Shear viscosity at $T_c$           & 0--0.2          \\
        $\eta/s$ slope    & Slope above $T_c$                  & 0--8 GeV$^{-1}$ \\
        $\eta/s$ crv      & Curvature above $T_c$              & $-1$ to $1$     \\
        $\zeta/s$ norm    & Bulk viscosity peak height         & 0--0.1          \\
        $\zeta/s$ width   & Bulk viscosity peak width          & 0--0.1 GeV      \\
        $\zeta/s$ temp    & Bulk viscosity peak location       & 150--200 MeV    \\
        $T_\text{switch}$ & Particlization temperature         & 135--165 MeV    \\
      \end{tabular}
    \end{column}
    \begin{column}{.4\textwidth}
      \textcolor{theme}{\scshape Important details:}
      \smallskip
      \begin{itemize}
        \small
        \item Parton width reparametrized:\\[1ex]
          $v = v_\text{min} + \X(v_\text{max} - v_\text{min})$\\[1ex]
          $v_\text{min} = 0.2$~fm,~ $v_\text{max} = w$\\[1ex]
        \item Parton sampling radius is \emph{not} equivalent to the proton radius
          in the proton c.o.m.\ frame, see\\
          \textcolor{theme}{\scriptsize PRC.94.024919}\\[1ex]
        \item Other parameters same as combined Pb+Pb analysis at 2.76 and 5.02 TeV
      \end{itemize}
    \end{column}
  \end{columns}
  \begin{center}
    \color{theme}
    500 design points per collision system, $\mathcal{O}(10^4)$ events per design point!
  \end{center}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.95\paperheight]{observables_design}
      };
    \node[anchor=east] at (current page.east) {
      \includegraphics[height=.95\paperheight]{observables_posterior}
      };
    \draw[<-] (current page.center) ++(-.75, 1.7) --
      node[above] {\footnotesize Prior}
      node[below] {\tiny (training data)}
      ++(1.5, 0);
    \draw[->] (current page.center) ++(-.75, -1.2) --
      node[above] {\footnotesize Posterior}
      node[below] {\tiny (samples)}
      ++(1.5, 0);
  \end{tikzpicture}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}
    \node {\includegraphics[height=.98\paperheight]{posterior}};
    \node (title) at (5.75, 3.5) {\color{theme}{\scshape \Large Bayesian posterior}};
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (-.35, .8);
    \draw<1>[->, thick, theme] (b3.west) to [out=180, in=90] (.1, -.95);
    \node<2>[xshift=-2.7cm, yshift=3.2cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<2>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_p}\\[2ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[.5ex]
        $dS/dy \sim \sqrt{T_A T_B}$
      };
    \node<3>[xshift=-1.05cm, yshift=1.5cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<3>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_parton_number}\\[2ex]
        \small Evidence for nucleon substructure $N_\text{partons} > 1$.\\
        \small Does not prefer a specific parton number.
      };
    \node<4>[xshift=.62cm, yshift=-.15cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<4>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_freestreaming}\\[2ex]
        \small Analysis cannot tolerate free-streaming\\
        \small times larger than ${\sim} 1$~fm/$c$
      };
    \node<5>[xshift=-.5cm, yshift=.9cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    \node<5>[below=.4cm of title, align=center] {
        \includegraphics[scale=.7]{posterior_structure}\\[2ex]
        \small Parton structure param.\ $\chi_\mathrm{struct} = 0.28_{-0.16}^{+0.17}$,\\
        \small Was used to reparametrize parton width as\\[.5ex]
        \small $v = v_\text{min} + \chi_\text{struct}(w - v_\text{min})$.\\[1ex]
        \small \hfill Let's revert $\chi_\text{struct}$ back to a width...
      };
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Nucleon size and shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
      \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Parton sampling radius\, $w = 1.04_{-0.15}^{+0.16}$~fm\\[.5ex]
          $^*$Note: the actual rms radius in the center of mass frame is somewhat smaller.\\[2ex]
        \item Parton width\, $v = 0.51_{-0.17}^{+0.19}$~fm\\[.5ex]
          (width of Gaussian constituents)\\[2ex]
        \item Results likely sensitive to model details,
          e.g.\ equation of state, pre-equilibirum dynamics and viscous
          corrections $\delta f$\\[2ex]
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape QGP medium properties}
\end{frame}

@@

\begin{frame}{\scshape Emulator validation}
  \begin{columns}
    \begin{column}{.35\textwidth}
      {\scshape Preprocessing}
      \begin{enumerate}
        \item log transform data
        \item subtract mean and divide out variance
        \item project onto principle component basis
      \end{enumerate}
      \medskip
      {\scshape k-fold cross validation}
      \begin{itemize}
        \item Subdivide design into $k$ partitions. Choose one for
          validation and use the rest for training. Repeat for all partitions.
      \end{itemize}
    \end{column}
    \begin{column}{.65\textwidth}
      \includegraphics[width=\textwidth]{validation_example}
    \end{column}
  \end{columns}
\end{frame}

>>>>

\title{Estimating nucleon substructure properties in a\\[.2ex]
unified model of p-Pb and Pb-Pb collisions}
\author[J.\ S.\ Moreland]{\scshape J.\ S.\ Moreland, J.\ E.\ Bernhard \& S.\ A.\ Bass}
\institute[Duke]{\scshape Duke University}
\date{\scshape 14 May 2018}

@@

\begin{frame}{\scshape Collectivity in small systems, is it flow?}
  \smallskip
  \begin{columns}[T]
    \begin{column}{.62\textwidth}
      \bigskip
      Important questions:\\
      \begin{itemize}
        \item Is hydro applicable to small collision systems?
        \item If so, can we describe small system collectivity using current hydro models?
      \end{itemize}
      \smallskip
      First question precludes the second, but also more difficult to answer.\\[1ex]
      Let's tackle the second question \textit{assuming} hydrodynamic models make
      sense down to length scales $\Delta x=.2$~fm.\\[1ex]
      Under this assumption, does a unified hydrodynamic description of p+A and A+A data exist?
    \end{column}
    \begin{column}{.3\textwidth}
      \centering
      \includegraphics[width=\columnwidth]{pbpb_corr2d}\\
      \includegraphics[width=\columnwidth]{ppb_corr2d}
    \end{column}
  \end{columns}

@@

\begin{frame}[t]{\scshape Nuclear structure}
  \begin{columns}[T]
    \begin{column}{.4\textwidth}
      \begin{figure}
        \includegraphics[width=.9\columnwidth]{pb208}\\
        $^{208}$Pb nucleus
      \end{figure}
    \end{column}
    \begin{column}{.6\textwidth}
      \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{itemize}
        \item Sample nucleon positions from spherical or deformed Woods-Saxon distributions
        \item Solid angles resampled to preserve minimum nucleon distance
          $d_\mathrm{min}$ [fm]
        \item Gaussian nucleons of width $w$ [fm]
      \end{itemize}
      \medskip
      \textcolor{theme}{This work:}
      \begin{itemize}
        \item Trade Gaussian nucleons for lumpy nucleons
      \end{itemize}
      \begin{tikzpicture}[absolute, overlay]
        \node (a) at (2, -.75) {\includegraphics[scale=.5]{gaussian_proton}};
        \node[right=of a.east] (b) {\includegraphics[scale=.5]{deformed_proton}};
        \draw[->, thick] (a) -- (b);
      \end{tikzpicture}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t, plain]{\scshape Nucleon substructure}
  \vspace{2em}
  \begin{columns}[t]
    \begin{column}{.2\textwidth}
      \centering \small Sampling radius
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw[thick] (0,0) circle [radius= 1cm] node (A) {\normalsize 1 fm};
          \draw[thick] (0,-2) circle [radius=.8cm] node (B) {\small .8 fm};
          \draw[thick] (0,-3.6) circle [radius=.6cm] node (C) {\scriptsize .6 fm};
          \draw [thick] (0,-4.8) circle [radius=.4cm] node (D) {\tiny .4 fm};
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.2\textwidth}
      \centering \small Constituent width
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0, 0) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.3) circle (.6cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-2.2cm] circle (.4cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.2cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.23\textwidth}
      \centering \small Constituent number
      \begin{figure}
        \begin{tikzpicture}[scale=.9]
          \draw [thick, dashed] (0,0) circle (1cm);
          \foreach \theta/\radius in {
            36/0.48, 72/0.6, 108/0.6, 140/0.36, 172/0.12,
            190/0.6, 240/0.36, 272/0.6, 308/0.48, 360/0.6
          }{
            \draw [thick] ({\theta}:\radius) circle (.3cm);
          }
          \draw [thick, dashed] (0, -2.2) circle (1cm);
          \foreach \theta/\radius in {
            0/.4, 65/.5, 115/.45, 190/.53, 240/.44, 310/.62
          }{
            \draw [thick] ({\theta}:\radius) [yshift=-2.2cm] circle (.3cm);
          }
          \draw [thick, dashed] (0, -4.4) circle (1cm);
          \foreach \theta in {0, 120, 240}{
            \draw [thick] ({\theta}:.39) [yshift=-4.4cm] circle (.3cm);
          }
        \end{tikzpicture}
      \end{figure}
    \end{column}
    \begin{column}{.37\textwidth}
      \centering
      \textcolor{theme}{Free parameters:}\\[1ex]
      \begin{itemize}
        \small
        \item Radius of Gaussian distribution used to sample
          constituent positions
        \item Gaussian constituent width
        \item Number of constituents in each nucleon
      \end{itemize}
      \bigskip
      \textcolor{theme}{Absent from this work:}\\[1ex]
      \begin{itemize}
        \small
        \item Spatial correlations,
          see talk by Alba Soto Ontoso
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Cross sections}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_participants}\\
        \small MC-Glauber cross sections\\
        (one constituent)
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{align*}
        P_\text{coll} &= 1 - \exp[-\sigma_\text{eff} T_\text{pp}(b)] \\
        \sigma_\text{nn}^\text{inel} &= \int 2\pi b\, db\, P_\text{coll}(b)
      \end{align*}
      \only<1>{\includegraphics<1>[scale=.8]{collision_profile}}
      \only<2>{
        \textcolor{theme}{This work:}
        \begin{equation*}
          P_\text{coll} \rightarrow 1 - \prod_{i,j=1}^{n_\text{part}}
          [1 - P_\text{coll}(b_{ij})]
        \end{equation*}
        Solve for effective cross section parameter $\sigma_\text{eff}$ numerically
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Participant thickness functions}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_thickness}\\
        \small Participant matter
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \centering \bigskip
      \textcolor{theme}{Original \trento\ model:}
      \begin{equation*}
        T_\text{nucleus}(x, y) = \sum\limits_{i=1}^{N_\text{part}}
        \gamma_i\, T_\text{proton}(x - x_i, y - y_i)
      \end{equation*}
      {\small Random weight $\gamma_i$ sampled from Gamma distribution with unit mean
      and variance $1/k$.}\\[2ex]
      \textcolor{theme}{This work:}
      \begin{equation*}
        \gamma_i\, T_\text{proton} \rightarrow \sum\limits_{j=1}^{N_\text{parton}}
        \gamma_j\,T_\text{parton}
      \end{equation*}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Entropy deposition}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_entropy}\\
        \small Entropy density
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Generalized Mean Ansatz:}
      \begin{equation*}
        \frac{dS}{d\eta} \propto T_R(T_A, T_B) \equiv
        \left(\frac{T_A^p + T_B^p}{2}\right)^{1/p}
      \end{equation*}
      \begin{equation*}
        T_R =
        \begin{cases}
          \max(T_A, T_B) & p \rightarrow +\infty, \\[.5ex]
          (T_A + T_B)/2 & p = +1, \\[.5ex]
          \sqrt{T_A T_B} & p = 0, \\[.5ex]
          2\, T_A T_B/(T_A + T_B) & p = -1, \\[.5ex]
          \min(T_A, T_B) & p \rightarrow -\infty.
        \end{cases}
      \end{equation*}
      \begin{center}
        \smallskip \small $T$ denotes \emph{participant} thickness function
      \end{center}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}[t]{\scshape Free streaming}
  \begin{columns}[T]
    \begin{column}{.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{trento_freestream}\\
        \small Arrows: fluid velocity\\weighted by energy density
      \end{figure}
    \end{column}
    \begin{column}{.5\textwidth}
      \bigskip \centering
      \textcolor{theme}{Pre-equilibrium phase:}
      \begin{itemize}
        \small
        \item Massless non-interacting parton gas matched to viscous hydrodynamics
          \textcolor{theme}{\scriptsize PRC.91.064906, PRC.80.034902}.
        \item Must reinterpret initial entropy density as initial gluon density,\,
          $dN_g/y \sim dS/dy$
        \item Initialize hydro with non-zero $u^\mu$ and $\pi^{\mu\nu}$
      \end{itemize}
      \medskip
      \includegraphics{coupling}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}[t]{\scshape Computer experiment design}
  \bigskip
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      \scriptsize
      \begin{tabular}{lll}
        Parameter         & Description                        & Range           \\
        \paddedhline
        Norm              & Overall normalization              & 12--28          \\
        $p$               & Entropy deposition parameter       & $-1$ to $+1$    \\
        $\sigmaf$         & Relative parton fluct. std.\       & 0--2            \\
        $w$               & Parton sampling radius             & 0.4--1.2 fm     \\
        $\X$              & Parton structure parameter         & 0--1            \\
        $\npartons$       & Number of partons                  & 1--10           \\
        $\dmin$           & Nucleon exclusion volume           & 0--4.9 fm$^3$   \\
        $\tau_{fs}$       & Free streaming time                & 0.1--1.5 fm/$c$ \\
        $\eta/s$ min      & Shear viscosity at $T_c$           & 0--0.2          \\
        $\eta/s$ slope    & Slope above $T_c$                  & 0--8 GeV$^{-1}$ \\
        $\eta/s$ crv      & Curvature above $T_c$              & $-1$ to $1$     \\
        $\zeta/s$ norm    & Bulk viscosity peak height         & 0--0.1          \\
        $\zeta/s$ width   & Bulk viscosity peak width          & 0--0.1 GeV      \\
        $\zeta/s$ temp    & Bulk viscosity peak location       & 150--200 MeV    \\
        $T_\text{switch}$ & Particlization temperature         & 135--165 MeV    \\
      \end{tabular}
    \end{column}
    \begin{column}{.4\textwidth}
      \textcolor{theme}{\scshape Important details:}
      \smallskip
      \begin{itemize}
        \small
        \item Recast constituent width $w$ as:\\[1ex]
          $w = w_\text{min} + \X(r - w_\text{min})$\\[1ex]
          $v_\text{min} = 0.2$~fm,~ $v_\text{max} = w$\\[1ex]
        \item Parton sampling radius is \emph{not} equivalent to the proton radius
          in the proton c.o.m.\ frame, see\\
          \textcolor{theme}{\scriptsize PRC.94.024919}\\[1ex]
        \item Other parameters same as combined Pb+Pb analysis at 2.76 and 5.02 TeV
      \end{itemize}
    \end{column}
  \end{columns}
  \begin{center}
    \color{theme}
    500 design points per collision system, $\mathcal{O}(10^4)$ events per design point!
  \end{center}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.95\paperheight]{observables_design}
      };
    \node[anchor=east] at (current page.east) {
      \includegraphics[height=.95\paperheight]{observables_posterior}
      };
    \draw[<-] (current page.center) ++(-.75, 1.7) --
      node[above] {\small Prior}
      node[below] {\scriptsize (training data)}
      ++(1.5, 0);
    \draw[->] (current page.center) ++(-.75, -1.2) --
      node[above] {\small Posterior}
      node[below] {\scriptsize (samples)}
      ++(1.5, 0);
  \end{tikzpicture}
\end{frame}

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.98\paperheight]{posterior}
    };
    \node[anchor=north, xshift=3cm, yshift=-.5cm] (title) at (current page.north) {
      \color{theme}{\scshape \Large Bayesian posterior}
    };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (2.6, .8);

    \draw<1>[->, thick, theme] (b3.west) to [out=180, in=90] (2.6, -.6);

    \node<2>[xshift=0cm, yshift=0cm, scale=.3] {
      \includegraphics[scale=.15]{magnifying-glass}
    };
    \node<2>[below=.4cm of title, align=center] {
        \includegraphics[width=.5\textwidth]{posterior_p}\\[1ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[.5ex]
        $dS/dy \sim \sqrt{T_A T_B}$
      };
    %\node<3>[xshift=-1.05cm, yshift=1.5cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    %\node<3>[below=.4cm of title, align=center] {
    %    \includegraphics[width=.5\textwidth]{posterior_parton_number}\\[2ex]
    %    \small Evidence for nucleon substructure, $N_\text{partons} > 1$.\\
    %    \small Does not prefer a specific constituent number.
    %  };
    %\node<4>[xshift=-1.6cm, yshift=1.0cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    %\node<4>[below=.4cm of title, align=center] {
    %    \includegraphics[scale=.7]{proton_posterior_shape}\\[2ex]
    %  };
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Nucleon size and shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
      \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Parton sampling radius,\\[.5ex]
          $\sigma_\mathrm{const} = 0.99_{-0.15}^{+0.17}$~fm\\[2ex]
        \item Parton (Gaussian constituent) width,\\[.5ex]
          $w_\mathrm{const} = 0.47_{-0.15}^{+0.20}$~fm\\[2ex]
        \item Results likely sensitive to model details,
          e.g.\ equation of state, pre-equilibrium dynamics and viscous
          corrections $\delta f$\\[2ex]
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape QGP medium properties}
  \begin{figure}
    \includegraphics[width=.9\textwidth]{region_shear_bulk}
  \end{figure}
  \begin{center}
    Pb-Pb at 2.76 and 5.02 TeV, better constraint on $\eta/s$ than p-Pb and Pb-Pb at 5.02 TeV
  \end{center}
\end{frame}

@@

\begin{frame}{\scshape Emulator validation}
  \begin{columns}
    \begin{column}{.35\textwidth}
      {\scshape Preprocessing}
      \begin{enumerate}
        \item subtract mean and divide out variance
        \item project onto principle component basis
      \end{enumerate}
      \medskip
      {\scshape k-fold cross validation}
      \begin{itemize}
        \item Subdivide design into $k$ partitions. Choose one for
          validation and use the rest for training. Repeat for all partitions.
      \end{itemize}
    \end{column}
    \begin{column}{.65\textwidth}
      \includegraphics[width=\textwidth]{validation_example}
    \end{column}
  \end{columns}
\end{frame}
